\plaintitle

### 2016-07-28 drafts/labor/introduction.tex
bibs and stuff
notes from meeting

\newcommand{\note}[1]{\onlyinsubfile{\ali{#1}}}
\section{Introduction}
The past decade has seen a flourishing of on--demand work
where the statuses of workers have become so fleeting that 
these workers
(known colloquially as ``Turkers'')
have been described as ``transient''
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that tasks can be accomplished by directing and managing this crowd of workers
has spurred the research and and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, seemingly ephemeral labor force.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using Turkers
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

@@

From various perspectives and with an eye toward myriad stakeholders,
this body of work has ostensibly sought to answer one overarching question:
What does the future hold for work and those that do it? % expand on ...?
To give several key examples,
the driving motivation behind much of the research in this space has led us to ask,
at a high level, three important questions:
\begin{enumerate}
  \item What are the (creative, cognitive, emotional) limits of crowdsourcing?
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of worker management and arrangement are viable (and moreover \textit{effective})?
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}.
    \note{these questions are all a little guilty of vagueness but this feels especially ``meh''}
\end{enumerate}

@@

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new
(indeed,
\citeauthor{crowdworkFuture}
in
\citeyear{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time),

% but not given as much weight as it perhaps could have been
\cite{crowdworkFuture}.
% ``Piecework'' here makes use of
% a term historically used to describe work done in the home,
% in manageable tasks,
% often involving clear instructions
% and payment only for work completed, not work done
% (the differentiation then being that
% one would be paid for the \textit{output} of the work,
% not the \textit{duration}).

@@

We'll look at a broad range of cases under a number of major themes
we propose as broadly describing the types of research being done in crowd work
and more generally in what we argue is contemporary piecework.
After validating this lens as a way of reasoning about on--demand labor,
we'll attempt to use this perspective to suggest areas of research worth anticipating,
and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications based on this research\dots \ali{???}

@@

>>>>

\newcommand{\note}[1]{\onlyinsubfile{\ali{#1}}}

\section{Introduction}
The past decade has seen a flourishing of on--demand work
where the statuses of workers have become so fleeting that 
these workers
(known colloquially as ``Turkers'')
have been described as ``transient''
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that tasks can be accomplished by directing and managing this crowd of workers
has spurred the research and and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, seemingly ephemeral labor force.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using Turkers
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

@@

From various perspectives and with an eye toward myriad stakeholders,
this body of work has ostensibly sought to answer one overarching question:
What does the future hold for work and those that do it? % expand on ...?
To give several key examples,
the driving motivation behind much of the research in this space has led us to ask,
at a high level, three important questions:
\begin{enumerate}
  \item What are the (creative, cognitive, emotional) limits of crowdsourcing? (what are the \textbf{complexity limits}) \note{(hospitals at high level?) -- team scaffolds} \note{why is there a high limit? is that different with crowds?}
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of worker management and arrangement are viable (and moreover \textit{effective})?
  \note{time in motion studies; job design; }
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}.
    \note{these questions are all a little guilty of vagueness but this feels especially ``meh''}
\end{enumerate}

\note{4 paragraphs on what happened in the above contexts; 2 paragraphs on best/worst outcomes \& why; ??? paragraphs on predictions for crowdsourcing}

@@

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new.
Indeed,
\citeauthor{crowdworkFuture}
in
\citeyear{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
% but not given as much weight as it perhaps could have been
\cite{crowdworkFuture}.
% ``Piecework'' here makes use of
% a term historically used to describe work done in the home,
% in manageable tasks,
% often involving clear instructions
% and payment only for work completed, not work done
% (the differentiation then being that
% one would be paid for the \textit{output} of the work,
% not the \textit{duration}).

@@

We'll look at a broad range of cases under a number of major themes
we propose as broadly describing the types of research being done in crowd work
and more generally in what we argue is contemporary piecework.
After validating this lens as a way of reasoning about on--demand labor,
we'll attempt to use this perspective to suggest areas of research worth anticipating,
and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications based on this research\dots \note{???}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
}
